---
title: "Working with ENCODE inside biOmics"
author: "Tiago Chedraoui Silva"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

This document describes how to search/download encode data using
biOmics package.
  
## Encode search
 You can easily search tcga samples using the `encodeSearch` function.
 Using a summary of roadmap datatabase, the function works with the
 following parameters:

*  accession
*  biosample
*  assay
*  lab
*  target
*  description
*  organism

Some examples of search are shown below
```{r, eval = FALSE}
query <- encodeSearch(accession = "ENCSR602PHV")
```

Obs: As these terms needs to be exact we validate user input before searching.

## Encode download
You can easily download roadmap data using the `encode.download` function.
 
```{r, eval = FALSE}
# get all sampples from the query and save into tcga folder
encodeDownload(query,path="tcga",type="fastq") 
```

Obs: The function will structure the folders to save the data as:
_Path given by the user/Experiment folder_
