---
title: "Working with roadmap inside biOmics"
author: "Tiago Chedraoui Silva"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

This document describes how to search/download roadmap data using biOmics package.
  
## Roadmap search
 You can easily search roadmap samples using the `search.roadmap` function.
 Using a summary of roadmap datatabase, the function works with the following parameters:

* samples
* experiment
* GEO.Accession 
* NA.Accession
* center 
* embargo.end.date 


```{r, eval = FALSE}
# get all H1 cell line and IMR90 cell line from platforms H3K4me1 H3K4me3
query <- roadmap.search(sample     = c("H1 cell line","IMR90 cell line"),
                          experiment = c("H3K4me1","H3K4me3")
                          )
```

Obs: As these terms needs to be exact we validate user input before searching.

## Roadmap download
You can easily download roadmap data using the `get.roadmap` function.
 
```{r, eval = FALSE}
# get all bed sampples from the query and save into rmap folder
roadmap.download(query,type="bed",path="rmap") 
```

Obs: The function will structure the folders to save the data as:
_Path given by the user/Experiment name/Sample name_
