---
title: "Working with TCGA inside biomics"
author: "Tiago Chedraoui Silva"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

This document describes how to search/download tcga data using biomics package.
  
## TCGA search
 You can easily search tcga samples using the `TCGAQuery` function.
 Using a summary of roadmap datatabase, the function works with the following parameters:

* tumor
* platform
* added.since
* added.up.to
* listSample
* level

Some examples of search are shown below
```{r, eval = FALSE}
query <- tcga.search(tumor="gbm",
                     added.since="01/01/2013",
                     added.up.to = "06/01/2013")

query <- tcga.search(tumor = "gbm", platform = "bio")

query <- tcga.search(tumor = "gbm", platform = "HumanMethylation450",level="3")

query <- tcga.search(listSample = "TCGA-61-1743-01A-01D-*")

query <- tcga.search(listSample = "TCGA-61-1743-01A-01D-0649-04")

query <- tcga.search(listSample = "TCGA-61-1743-01A-01D-0649-04", level="3")

query <- tcga.search(listSample = "TCGA-61-1743-01A-01D-0649-04",
                     tumor = "OV", platform = "CGH-1x1M_G4447A"
                     )
```

Obs: As these terms needs to be exact we validate user input before searching.

## Roadmap download
You can easily download roadmap data using the `tcga.download` function.
 
```{r, eval = FALSE}
# get all sampples from the query and save into tcga folder
tcga.download(query,path="tcga") 
```

Obs: The function will structure the folders to save the data as:
_Path given by the user/Experiment folder_
